Standalone Tactics using OpenTheory

### 2012-01-24 paper.tex
reworking the introduction
move main novelty further up. split examples into categories.

For instance, Kumar and Weber~\cite{DBLP:conf/itp/KumarW11} and Kun\v{c}ar~\cite{DBLP:conf/itp/Kuncar11} give independent integrations of a quantified boolean formula solver into a higher-order logic based system (HOL4 in one case and HOL Light in the other).
Weber and Amjad~\cite{weber09efficiently} give high-performance integrations of SAT solvers into three HOL-based systems (HOL4, HOL Light, and Isabelle/HOL); each integration requires a separate implementation.
<Metis integrated many times separately; currenty HOL4 version is very old and upgrading would be painful>
<Sledgehammer~\cite{DBLP:journals/japll/MengP09,Paulson_threeyears} is available for Isabelle only, but the ideas behind it don't intrinsically exclude HOL4, HOL Light, etc.>
<TFL, function package,>
Certain kinds of functionality, or improvements in functionality (e.g. Isabelle function package over TFL) become restricted to a single proof assistant unnecessarily.
<datatype packages>
<arithmetic decision procedures>

@@

\OpenTheory~\cite{hurd2009} is designed for storing and sharing higher-order logic theories.
By using \OpenTheory to communicate to tactics (sending goals and receiving proofs), we obtain
\begin{enumerate}
\item
A standard format (article files) for goals and proofs, and
\item
An extensible way to fix the meaning of constants and type definitions.
\end{enumerate}

@@

\section{Conclusions}

Additional (non-proof) work tactics might also do needs to be represented on another channel.

@@

>>>>

It makes sense to speak of similar functionality in different systems not just because they use roughly the same logic, but also because there is a shared base of concepts: booleans, inductive datatypes, recursive functions, natural numbers, lists, sets, etc.  
The \OpenTheory standard library~\cite{DBLP:conf/nfm/Hurd11} formalises this shared base, using \OpenTheory~\cite{hurd2009}, a format designed for storing and sharing higher-order logic theories.
We use \OpenTheory to communicate to tactics (sending goals and receiving proofs), and thereby obtain
\begin{enumerate}
\item
A standard format (article files) for goals and proofs, and
\item
An extensible way to fix the meaning of constants and type definitions.
\end{enumerate}

Examples of duplicate effort include the integration of external tools into HOL-based provers.
For instance, Kumar and Weber~\cite{DBLP:conf/itp/KumarW11} and Kun\v{c}ar~\cite{DBLP:conf/itp/Kuncar11} give independent integrations of a quantified boolean formula solver into a higher-order logic based system (HOL4 in one case and HOL Light in the other).
Weber and Amjad~\cite{weber09efficiently} give high-performance integrations of SAT solvers into three HOL-based systems (HOL4, HOL Light, and Isabelle/HOL); each integration requires a separate implementation.
Sledgehammer~\cite{DBLP:journals/japll/MengP09,Paulson_threeyears} is only available for Isabelle/HOL, but would be useful if available for other provers.

Besides duplicate initial effort, costs of maintenance can be multiplied over different provers, and improvements in functionality can become restricted to single prover unnecessarily.
For instance, Hurd's first-order prover, Metis~\cite{DBLP:conf/cade/Hurd02}, is integrated in at least three HOL-based provers, but the HOL4 version is very old compared to the latest version in Isabelle/HOL.
Another example is a package for defining recursive functions, TFL <ref>, which was originally written within both Isabelle/HOL and HOL4 <and others?> but was recently superceded by Krauss's function package <ref> in Isabelle/HOL only.
Krauss's improvements ought to be applicable to other HOL-based provers <really?>, but a direct re-implementation would require substantial effort.

@@

@@

\section{Conclusions}
Additional (non-proof) work tactics might also do needs to be represented on another channel.

@@

Other examples of functionality that could usefully be made prover-independent include packages for defining recursive datatypes or for solving classes of arithmetic problems.
